On the presentation of orthogonal groups over polynomial rings

### 2019-07-26 dl-paper.tex
Minor fix

\begin{theorem}[Stein] \label{thmStein} One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \overline{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{theorem} \begin{proof} See~\cite[Theorem~2.4]{Ste73}. \end{proof}

>>>>

\begin{theorem*}[Stein] One has $\overline{\St}(\Phi, A, M) = U(\Phi^+, M) \cdot \overline{H}(\Phi, A, M) \cdot U(\Phi^-, M).$ \end{theorem*} \begin{proof} See~\cite[Theorem~2.4]{Ste73}. \end{proof}
